Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-13 ms.tex
adjusting ti

The minimum heating rate for thermal stability (eq.~[\ref{eq:cooling2}]) corresponds to maximum thermally-stable accretion rate,
\begin{align}
  \frac{\dot{M}_{\rm TI}}{\dot{M}_{\rm edd}} \simeq {\rm
    min}\begin{cases}
    2\times 10^{-4} \eta_{0.02}^{0.47} M_{\bullet,8}^{0.36} &, \text{core}, \zeta > \zeta_c\\
    4\times 10^{-6}\eta_{0.02}M_{\bullet,8}^{-0.37} &, \text{core}, \zeta < \zeta_c \\
    7\times 10^{-5} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.28}    &, \text{cusp}, \zeta > \zeta_c\\
    1\times 10^{-4}\eta_{0.02}&, \text{cusp}, \zeta < \zeta_c
  \end{cases}
  \label{eq:Mdotmax}
\end{align}
where the first line for each case is derived using equation
(\ref{eq:eddr_analytic}) to calculate $\dot{M}(v_{\rm TI})$, and
the second line corresponds to the low wind heating limit $\zeta \ll
\zeta_c$.  $\zeta_c$ is calculated using the empirical correlation for
core galaxies $r_{b}/r_{\rm inf} \approx 7.6M_{\bullet,8}^{-0.2}$ which
follows from equation (\ref{eq:rsoi}) and the $r_b-M_{\bullet}$
correlation derived from the results of \citet{LauerFaber+:2007a}.

>>>>

The minimum heating rate for thermal stability (eq.~[\ref{eq:cooling2}]) corresponds to maximum thermally-stable accretion rate,
\begin{align}
  \frac{\dot{M}_{\rm TI}}{\dot{M}_{\rm edd}} \simeq {\rm
    min}\begin{cases}
    2\times 10^{-4} \eta_{0.02}^{0.47} M_{\bullet,8}^{0.36} &, \text{core}, \zeta > \zeta_c\\
    4\times 10^{-6}\eta_{0.02}M_{\bullet,8}^{-0.37} &, \text{core}, \zeta < \zeta_c \\
    8\times 10^{-5} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.28}    &, \text{cusp}, \zeta > \zeta_c\\
    1\times 10^{-4}\eta_{0.02}&, \text{cusp}, \zeta < \zeta_c
  \end{cases}
  \label{eq:Mdotmax}
\end{align}
where the first line for each case is derived using equation
(\ref{eq:eddr_analytic}) to calculate $\dot{M}(v_{\rm TI})$, and
the second line corresponds to the low wind heating limit $\zeta \ll
\zeta_c$.  $\zeta_c$ is calculated using the empirical correlation for
core galaxies $r_{b}/r_{\rm inf} \approx 7.6M_{\bullet,8}^{-0.2}$ which
follows from equation (\ref{eq:rsoi}) and the $r_b-M_{\bullet}$
correlation derived from the results of \citet{LauerFaber+:2007a}.
